Spin canonical rings of log stacky curves

### 2015-07-02 stacky_write_up/spin_cring.tex
g0 intro revision

\section{Genus Zero}
\label{sec:g_0}
We will prove that if $(\sx , \Delta, \halfcan)$ is a log spin curve and
$\sx$ has signature $\sigma = (0; e_1, \ldots , e_r; \delta)$,
then $R(\sx , \Delta, L)$ is generated in degree at most $e := \max(
5, e_1, \ldots, e_r)$ with relations generated in degree at most $2e
$, so long as $\sigma$ does not lie in the finite list given in Table ~\ref{table:g-0-exceptional}.

As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even, so we can reduce to two cases: $\delta \geq 2$ and $\delta = 0$.
In the former case, $\halfcan$ is linearly equivalent to an effective divisor, so the
result of Theorem \ref{thm:main} follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1} to add the necessary fractional points.
On the other hand, the proof when $\delta =
0$ is a more involved, and we dedicate the remainder of this section to proving it through the following steps: 
characterizing saturations points (Subsection ~\ref{ssec:g_0_saturation}), describing
base cases (Subsection ~\ref{ssec:g_0_base}), presenting exceptional
cases (Subsection ~\ref{ssec:g-0-exceptional}), and applying inductive Lemmas ~\ref{lem:sat-3} and ~\ref{lem:raise-stacky-order} to prove \todo{synonym for prove, so its not repeated twice in this sentence?} Theorem \ref{thm:main} when $\delta = 0$ (Subsection ~\ref{ssec:g-0-main}.\todo{Peter: I made some changes to this last paragraph (gramatical and stylistic-not mathematical).  See if you like them.}
%before proving the main theorem in full for all $\delta$ in
%Subsection ~\ref{ssec:g-0-main}.

>>>>

\section{Genus Zero}
\label{sec:g_0}
We will prove that if $(\sx, \Delta, \halfcan)$ is a log spin
curve and $\sx$ has signature $\sigma = (0; e_1, \ldots, e_r;
\delta)$, then $R(\sx, \Delta, L)$ is generated in degree at most
$e := \max(5, e_1, \ldots, e_r)$ with relations generated in degree
at most $2e$, so long as $\sigma$ does not lie in the finite list
given in Table ~\ref{table:g-0-exceptional}.

As noted in Remark ~\ref{rem:delta-not-1}, $\delta$ is even. Thus,
we can reduce the problem into two cases: $\delta \geq 2$ and
$\delta = 0$. In the former case, $\halfcan$ is linearly equivalent
to an effective divisor, so the result of Theorem \ref{thm:main}
follows immediately by repeatedly applying Lemma ~\ref{lem:sat-1}
to add the necessary stacky points. On the other hand, the proof
when $\delta = 0$ is more involved. We dedicate the remainder of
this section to that case in the following steps: characterizing
saturations points (Subsection ~\ref{ssec:g_0_saturation}),
describing base cases (Subsection ~\ref{ssec:g_0_base}), and
presenting exceptional cases (Subsection ~\ref{ssec:g-0-exceptional}).
Finally, we apply inductive processes using Lemma ~\ref{lem:sat-3}
and Lemma ~\ref{lem:raise-stacky-order} to prove the main theorem
in the full genus zero case (Subsection ~\ref{ssec:g-0-main}).
